Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Add equation for kernel function

A more flexible strategy uses what is known as \emph{Bayesian
  quadrature} \cite{Diaconis:1988uo,OHagan:1991tx} to estimate $Z$.
Bayesian quadrature allows us to compute a posterior distrbution over
$Z$ by placing a Gaussian Process (GP) \cite{Rasmussen:2006vz} prior
on the function $S$ and evaluating $S$ at a particular set of
points. However, this strategy has its difficulties: while in our
case, $S$ is a non-negative likelihood function, GP regression
enforces no such constraint.

\cite{Osborne:2012tm} give a method which more often (but not
entirely) avoids this problem. Instead of placing a prior over $S$, a
prior is instead placed over $\log S$, thus ensuring that $S=e^{\log
  S}$ will be positive\footnote{In practice, as in
  \cite{Osborne:2012tm}, we use the transform of $\log(S+1)$.}:
\begin{equation*}
  E[Z\ \vert \ \log S]=\int_{\log S}\left(\int_R \exp(\log{S(X_b,X_R)})p(R)\ \mathrm{d}R\right)\mathcal{N}\left(\log{S}\ \vert \ \mu_{\log S}, \Sigma_{\log S}\right)\ \mathrm{d}\log S
\end{equation*}
where $\mu_{\log S}$ and $\Sigma_{\log S}$ are the mean and
covariance, respectively, of the GP regression over $\log S$ given
$\mathbf{R}$. We approximate this according to the method given in
\cite{Osborne:2012tm}:
\begin{equation}
  \mu_Z=E[Z\ \vert \ S, \log S, \Delta_c] \approx \int_R \mu_{S}(1 + \mu_\Delta) p(R)\ \mathrm{d}R 
  \label{eq:bq-Z-mean}
\end{equation}
where $\mu_S$ is the mean of a GP regression over $S$ given
$\mathbf{R}$; and $\mu_{\Delta_c}$ is a regression over
$\Delta_c=\mu_{\log S} - \log \mu_S$ given $\mathbf{R}_c$, which
consists of $\mathbf{R}$ and a set of intermediate \emph{candidate
  points}\footnote{These candidate points do not require evaluating
  the true $S$, only the GP estimates of $S$ and $\log S$.} $c$ as
described in \cite{Osborne:2012tm}. The variance of the estimate of
$Z$ is given by:
\begin{equation}
  \sigma_Z=\mathrm{Var}(Z\ \vert \ S, \log S, \Delta_c) = \int_R\int_{R^\prime} \mu_S(R)\mu_S(R^\prime) \Sigma_{\log S}(R, R^\prime)p(R)p(R^\prime)\ \mathrm{d}R\ \mathrm{d}R^\prime
  \label{eq:bq-Z-var}
\end{equation}

>>>>

A more flexible strategy uses what is known as \emph{Bayesian
  Quadrature} \cite{Diaconis:1988uo,OHagan:1991tx} to estimate $Z$.
Bayesian Quadrature allows us to compute a posterior distrbution over
$Z$ by placing a Gaussian Process (GP) prior on the function $S$ and
evaluating $S$ at a particular set of points. Because our data is
circular, we can use a periodic kernel \cite{Rasmussen:2006vz}:
\begin{equation}
k(R, R^\prime)=h^2\exp\left(-\frac{2\sin^2\left(\frac{1}{2}(R-R^\prime)\right)}{w^2}\right)
\end{equation}

Bayesian Quadrature has its difficulties, however. While in our case
$S$ is a non-negative likelihood function, GP regression enforces no
such constraint. In an effort to avoid this problem,
\cite{Osborne:2012tm} give a method which involves instead placing a
prior over the log liklihood\footnote{In practice, as in
  \cite{Osborne:2012tm}, we use the transform of $\log(S+1)$.}, thus
ensuring that $S=e^{\log S}$ will be positive\footnote{We are not
  guaranteed positivity, however, the approximation to the integral
  over $\log S$ (Equation \ref{eq:bq-Z-mean}) requires computing
  $\mu_S$, which may have nonpositive segments.}:
\begin{equation*}
  E[Z\ \vert \ \log S]=\int_{\log S}\left(\int_R \exp(\log{S(X_b,X_R)})p(R)\ \mathrm{d}R\right)\mathcal{N}\left(\log{S}\ \vert \ \mu_{\log S}, \Sigma_{\log S}\right)\ \mathrm{d}\log S
\end{equation*}
where $\mu_{\log S}$ and $\Sigma_{\log S}$ are the mean and
covariance, respectively, of the GP regression over $\log S$ given
$\mathbf{R}$. We approximate this according to the method given in
\cite{Osborne:2012tm}:
\begin{equation}
  \mu_Z=E[Z\ \vert \ S, \log S, \Delta_c] \approx \int_R \mu_{S}(1 + \mu_\Delta) p(R)\ \mathrm{d}R 
  \label{eq:bq-Z-mean}
\end{equation}
where $\mu_S$ is the mean of a GP regression over $S$ given
$\mathbf{R}$; and $\mu_{\Delta_c}$ is a regression over
$\Delta_c=\mu_{\log S} - \log \mu_S$ given $\mathbf{R}_c$, which
consists of $\mathbf{R}$ and a set of intermediate \emph{candidate
  points}\footnote{These candidate points do not require evaluating
  the true $S$, only the GP estimates of $S$ and $\log S$.} $c$ as
described in \cite{Osborne:2012tm}. The variance of the estimate of
$Z$ is given by:
\begin{equation}
  \sigma_Z=\mathrm{Var}(Z\ \vert \ S, \log S, \Delta_c) = \int_R\int_{R^\prime} \mu_S(R)\mu_S(R^\prime) \Sigma_{\log S}(R, R^\prime)p(R)p(R^\prime)\ \mathrm{d}R\ \mathrm{d}R^\prime
  \label{eq:bq-Z-var}
\end{equation}
